Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-25 manuscript/manuscript.tex
Changes in manuscript

The equation \ref{eq:shell-pot} allows to easily obtain the exact gravity field generated by a spherical shell with a variable density in depth on any outside point located in the $z$ axe.
Due to the rotational symmetry along any axe that passes through the centre of the shell, the potential in equation \ref{eq:shell-pot} reassembles the gravity field on any outside point at distance $r$ from the its centre.

For any density $\rho(r')$, the gradient and Marussi tensor components can be obtained as \citet{Grombein2013} does.
Only the vertical gradient component ($g_z$) and the diagonal Marussi tensor components ($g_{xx}$, $g_{yy}$, $g_{zz}$) are non zero, and can be easily determined from the potential $V_\text{sh}$:

\todo{corregir esto y explicar mejor}

@@

For practical purposes we are going to obtain the gravity potential for three different functions in the perspective of their variation in $r'$: a linear, an exponential and a discontinuous density function.

@@

The second term on equation \ref{eq:shell-pot-linear} reassembles the potential generated by a spherical shell with homogeneous density $\rho = b$ \citep{Mikuska2006,Grombein2013}.
So, this potential can be read as the combination of a spherical shell with the later homogeneous density and the same shell with variable density $\rho(r') = ar'$.

@@

Although it's a Python library, the core functions of the computation are written in Cython, a superset of Python language that allows to generate efficient C code through the Cython compiler.
This produces a precompiled library whose functions and classes can be called from regular Python code, what allowed us to make it compatible with the preexisting open-source library Fatiando a Terra \citep{Uieda2013}.

@@

Instead of increasing the GLQ orders to improve the accuracy, what leads to a more time consuming computation, adaptive discretization algorithms have been applied in previous works \citep{Li2011, Uieda2016}.
They essentially consist in dividing the tesseroid based on a ratio between its size and the distance between its geometric centre and the computation point.

In order to make the computation more efficient, we use only second order GLQ for each integration, and we ensure the accuracy of the method through the application of the modified adaptive discretization algorithm developed by \citet{Uieda2016}.
Given an arbitrary tesseroid, \citet{Uieda2016} redefined its dimensions: $L_\lambda$, $L_\phi$ and $L_r$, where the former ones are the arc-distances measured along its top surface and $L_r$ is the difference between the radii of the top and bottom surfaces.
We must check that the following inequality is satisfied:

>>>>

The equation \ref{eq:shell-pot} allows to easily obtain the exact gravity field generated by a spherical shell with a variable density in depth on any outside point located in the $z$ axe.
Due to the rotational symmetry along any axe that passes through the centre of the shell, the integral in equation \ref{eq:shell-pot} reproduces the gravity potential field on any outside point at distance $r$ from the its centre.

The gradient and the Marussi tensor derived from potentials that depends solely on $r$ has only a few non zero components: the vertical component of the gradient ($g_z$) and the diagonal components of the tensor ($g_{xx}$, $g_{yy}$, $g_{zz}$).
They can be easily obtained as \citet{Grombein2013} does, even for any density function $\rho(r')$ of our choice:

@@

For practical purposes we are going to obtain the gravity potential for three different functions from the perspective of their variation in $r'$: a linear and an exponential density function.

@@

The second term on equation \ref{eq:shell-pot-linear} reproduces the potential generated by a spherical shell with homogeneous density $\rho = b$ \citep{Mikuska2006,Grombein2013}.
So it can be read as the combination of a spherical shell with the later homogeneous density and the same shell with variable density $\rho(r') = ar'$.

@@

Although it's a Python library, the core functions of the computation are written in Cython, a superset of Python language that allows to generate efficient C code through the Cython compiler.
This produces a precompiled library whose functions can be called from regular Python code, what allowed us to make it compatible with the preexisting open-source library Fatiando a Terra \citep{Uieda2013}.

@@

Instead of increasing the GLQ orders to improve the accuracy, what leads to a more time consuming computation, adaptive discretization algorithms have been applied in previous works \citep{Li2011, Uieda2016}.
They essentially consist in dividing the tesseroid based on a ratio between the distance from its geometric centre to the computation point and its dimensions.

In order to make the computation more efficient, we use only second order GLQ for each integration while we ensure the accuracy of the method through the application of the modified adaptive discretization algorithm developed by \citet{Uieda2016}.
Given an arbitrary tesseroid, \citet{Uieda2016} redefined its dimensions: $L_\lambda$, $L_\phi$ and $L_r$, where the former ones are the arc-distances measured along its top surface and $L_r$ is the difference between the radii of the top and bottom surfaces.
We must check that the following inequality is satisfied:
